analyze_growth

### 2024-10-09 smelt_2019_allseasons/analyze_growth.Rmd
Added code to save Rdata file
Calculated emmeans for FCCL

@@

#### Plot CI and RE
##### m1
```{r}
library(multcomp)
m1.emm <- emmeans(m1, "Season")
plotm1 = plot(m1.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m1 = cld(m1.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm1) %>%
  mutate(.group = gsub(" ", "", .group))

(plot_season_k <- ggplot(data = letter_m1,) + 
   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +

@@

##### m2
```{r}
library(multcomp)
m2.emm <- emmeans(m2, "Season")
plotm2 = plot(m2.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m2 = cld(m2.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm2) %>%
  mutate(.group = gsub(" ", "", .group))

@@

#### Export data and figures
```{r}
# emmeans results -------
write_csv(letter_m1, "smelt_2019_allseasons/data_clean/emmeans_RV_m1.csv")
write_csv(letter_m2, "smelt_2019_allseasons/data_clean/emmeans_RV_m2.csv")

@@

# plots in Rdata for Britt -------
save(plot_Site_k, plot_season_k, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")

>>>>

Make a FCCL set of data
```{r}
data2 <- read_csv(here(root,"data_clean","clean_smelt_cf_2019.csv")) %>%
  # filter(!(grepl("FCCL", Cage) & Season == "Winter")) %<%
  filter(!(Cage %in% c("A", "E","F") & Season == "Winter")) %>%
  filter(!(Site == "RV" & is.na(Cage))) %>%
mutate(Season = factor(Season)) %>%
  mutate(CageRep = paste0(Season, "_", Site, "_", Cage))

FCCL_fish <- data2 %>%
  filter(!Site %in% c("SM", "Yolo", "DWSC")) %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K")) %>%
  mutate(K_Pre = case_when(Season == "Fall"~ 0.7214667,
                         Season == "Summer" ~ 0.6626667,
                         Season == "Winter" ~ K_Pre),
         Weight_g_Pre = case_when(Season == "Fall" ~ 1.7213333,
                                Season == "Summer" ~ 0.8206667,
                                Season == "Winter" ~ Weight_g_Pre)) %>%
  mutate(deltaK = (K_Post - K_Pre)/K_Pre,
         deltaWt = (Weight_g_Post - Weight_g_Pre)/Weight_g_Pre) %>%
   filter(Site == "FCCL") %>%
  mutate(Season = factor(Season, levels = c("Winter", "Summer", "Fall"))) %>%
  filter(!is.na(deltaK))

FCCL_sumfall <- filter(FCCL_fish, Season != "Winter") 
FCCL_sumfall$Season = factor(FCCL_sumfall$Season, levels = c("Summer", "Fall"))
```

@@

# Effect of season at FCCL
```{r}
# CF
m1_FCCL <- lmer(deltaK ~ Season + (1|CageRep), data = FCCL_fish)
summary(m1_FCCL)
anova(m1_FCCL,type =2)
plot(m1_FCCL)

plot(m1_FCCL)
resid.m1F <- resid(m1_FCCL, type = "pearson")
par(mfrow = c(2,2))
plot(resid.m1F)
hist(resid.m1F)
qqnorm(resid.m1F)
plot(FCCL_fish$Season, resid.m1F)

# Weight
m2_FCCL <- lmer(deltaWt~ Season + (1|CageRep), data = FCCL_fish)
summary(m2_FCCL)
plot(m2_FCCL)

plot(m2_FCCL)
resid.m2F <- resid(m2_FCCL, type = "pearson")
par(mfrow = c(2,2))
plot(resid.m2F)
hist(resid.m2F)
qqnorm(resid.m2F)
plot(FCCL_fish$Season, resid.m2F)
```

#### Plot CI and RE
##### m1
```{r}
library(multcomp)
m1.emm <- emmeans(m1, "Season")
plotm1 = plot(m1.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m1 = cld(m1.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm1) %>%
  mutate(.group = gsub(" ", "", .group))%>%
  mutate(Site = "RV")

(plot_season_k <- ggplot(data = letter_m1) + 
   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +

@@

##### m2
```{r}
library(multcomp)
library(emmeans)
m2.emm <- emmeans(m2, "Season")
plotm2 = plot(m2.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m2 = cld(m2.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm2) %>%
  mutate(.group = gsub(" ", "", .group)) %>%
  mutate(Site = "RV")

@@

##### FCCL
```{r}
# Weight
m1.FCCL.emm <- emmeans(m1_FCCL, "Season")
plotm1_FCCL = plot(m1.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m1_FCCL = cld(m1.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm1_FCCL) %>%
  mutate(.group = gsub(" ", "", .group)) %>% 
  mutate(Site = "FCCL")

letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)

# K
m2.FCCL.emm <- emmeans(m2_FCCL, "Season")
plotm2_FCCL = plot(m2.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
letter_m2_FCCL = cld(m2.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
  left_join(plotm2_FCCL) %>%
  mutate(.group = gsub(" ", "", .group)) %>%
  mutate(Site = "FCCL")

letter_m2_emm_all <- rbind(letter_m2_FCCL, letter_m2)
```

#### Export data and figures
```{r}
# emmeans results -------
write_csv(letter_m1, "smelt_2019_allseasons/data_clean/emmeans_RV_m1.csv")
write_csv(letter_m2, "smelt_2019_allseasons/data_clean/emmeans_RV_m2.csv")
write_csv(letter_m1_emm_all, "smelt_2019_allseasons/data_clean/emmeans_RV_FCCL_m1.csv")
write_csv(letter_m2_emm_all, "smelt_2019_allseasons/data_clean/emmeans_RV_FCCL_m2.csv")

@@

# plots in Rdata for Britt -------
save(plot_Site_k, plot_season_k, letter_m3, letter_m1, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")
